%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  New template code for TAMU Theses and Dissertations starting Fall 2016.  
%
%
%  Author: Sean Zachary Roberson
%  Version 3.17.09
%  Last Updated: 9/21/2017
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                           ABSTRACT 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter*{ABSTRACT}
\addcontentsline{toc}{chapter}{ABSTRACT} % Needs to be set to part, so the TOC doesnt add 'CHAPTER ' prefix in the TOC.

\pagestyle{plain} % No headers, just page numbers
\pagenumbering{roman} % Roman numerals
\setcounter{page}{2}

\indent The LHCb experiment has reported slight discrepancies in the ratio in which B mesons decay to muons and electrons. some of these theories attempting to explain these anomalies theorize the existence of new particles beyond the standard model. This study performs a search for a heavy neutral gauge boson at the LHC with the CMS experiment. This Z' boson is assumed to couple mostly to third generation fermions, specifically b-quarks. The main production channel is b-quark fusion. Furthermore, since the b-quark PDF's are at least 10 times lower when compared to the gluon PDF's, we take advantage of the large contribution of bottom quarks coming from gluon-splitting to Z' production. In short, a study for Z'$\rightarrow b\bar{b}$ decays is proposed. The final state consists of 4 b jets, with the two extra jets coming from the initial gluon splitting. Results are correspond to 27.27 $fb^{-1}$ of proton-proton collision data recorded by the CMS detector at the LHC with a center-of-mass-energy of 13 TeV during 2016.


 

\pagebreak{}
